Results

### 2023-02-15 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
added flexer regression (H7b)

>>>>

[ HIER FEHLT NOCH DIE ORDINALE REGRESSION ]

Last, we investigated whether SVs are associated with ER flexibility.
We conducted a logistic regression to inspect whether participants' individual $slopes$ and $intercepts$ of ordered SVs could predict their ER flexibility score.
We found neither a significant associations between $slopes$ of SVs and FlexER score (`r papaja::apa_print(Flex_LM)$full_result$slope`, `r papaja::apa_print(Flex_LM_BF)$full_result$slope`), nor between $intercepts$ and FlexER score (`r papaja::apa_print(Flex_LM)$full_result$intercept`, `r papaja::apa_print(Flex_LM_BF)$full_result$intercept`).
However, model fit was relatively low (`r papaja::apa_print(Flex_LM)$full_result$modelfit$r2`).
